Network Configuration Synthesis with Abstract Topologies

### 2016-11-08 paper/abstraction/appendix.tex
clean up substitution proof

\documentclass[twocolumn]{sig-alternate-10pt}
%\documentclass[twocolumn]{article}
%\documentclass[10pt]{sigalternate052015}

@@

@@

\onecolumn
\section{Definitions}

@@

The full \sysname syntax as well as expansions from constraints into regular expressions are shown in Figure~\ref{fig:syntax}. The language includes constraints of the form $\CD{\Agg(pfx, \ensuremath{r_1 \rightarrow r_2})}$ that say that aggregation for summary prefix $\CD{pfx}$ will occur from any single location matching $\CD{\ensuremath{r_1}}$ to any location matching $\CD{\ensuremath{r_2}}$.

@@

We define syntax for an abstraction of BGP configurations -- called ABGP -- in Figure~\ref{fig:abgp-syntax}. An ABGP policy consists of a map from topology locations $l$ to router configurations $rc$. Each router configuration $rc$ is a sequence of prefix (templates) $t$ and their corresponding prefix configuration $pc$. A prefix configuration $pc$ is a sequence of match actions $ma$. Each match action $ma$ consists of a preference value $n$, followed by a set of peers $ns$ and community value (\IE, state of the product graph) $n$, and the exports the route to a new set of neighbors $ns$ and updates the community value $n$.

@@

We assume a particular router $l$ appears at most once in any abgp specification.
An abgp configuration is a partial function from router to prefix configuration.
We write $abgp(l)$ to apply such a config to a router location $l$.
%
We often build configs using set-builder notation.  For instance,
$\{l \rightarrow rc ~\vert~ l \in V \wedge p(l,rc)\}$ denotes the abgp policy

where $l_1, ..., l_k$ are the nodes in the topology
and each $rc_{ij}$ satisfies $p(l_i,rc_{ij})$. Similarly for $rc$.

@@

The function $compile_{ABGP}$ then takes tuples of $(t_i, PG_i, ord_i)$ and returns an ABGP policy. It looks at each incoming neighbor with the same community state $q_n$ and matches any of those neighbor with the preference provided by the ordering $ord$ obtained from the search for local preferences. It then exports this advertisement to each adjacent peer along an outgoing edge and adds the community value for the current state $q_m$.

@@

Here we define what it means to concretize an abstract \sysname policy. 
Concretization takes as input, a policy and a context $\Gamma$ mapping from a template prefix to a set of pairs of a concrete prefix and a concrete location where the prefix is owned.

\[ \begin{array}{lcl}
  con(\emptyset,\Gamma)                        & = & \emptyset \\
  con(l,\Gamma)                                & = & \Sigma ~ f^{-1}(l) \\
  con(r_1 \cup r_2,\Gamma)                     & = & con(r_1,\Gamma) \cup con(r_2,\Gamma) \\
  con(r_1 \cap r_2,\Gamma)                     & = & con(r_1,\Gamma) \cap con(r_2,\Gamma) \\
  con(!r,\Gamma)                               & = & !con(r,\Gamma) \\
  con(r^*,\Gamma)                              & = & con(r,\Gamma)^* \\
  con(pfx \Rightarrow r_1, \dots, r_k,\Gamma)  & = & pfx \Rightarrow con(r_1,\Gamma), \dots, con(r_k,\Gamma) \\
  con(\$x \Rightarrow r_1, \dots, r_k,\Gamma)  & = & \{ pfx \Rightarrow con(r_1,\Gamma) \cap \textbf{end}(l), \dots, \\
  & & ~~~~~~~~~~~~~~~ con(r_k,\Gamma) \cap \textbf{end}(l) ~\vert~ (pfx,l) \in \Gamma(x) \} \\
\end{array} \]

For each regular expression $r$, we replace each abstract location with the sum over its corresponding concrete locations under the inverse homomorphism $f^{-1}$. For each template variable, we replace it with a new entry for each of its corresponding concrete values under the supplied mapping $\Gamma$. We also intersect the resulting concretized regular expression with $\textbf{end}(l)$ to capture the fact that traffic is owned by the concrete location $l$. \textbf{Note}: we need the side condition that $\textbf{end}(l) \cap con(r_i,\Gamma) \neq \emptyset$ if $con(r_i,\Gamma) \neq \emptyset$.
We can also define concretization over the ABGP policy as:

\[ \begin{array}{lcl}
     con(l_1 \rightarrow {rc}_1, ~\dots,~ l_k \rightarrow {rc}_k,\Gamma,G) 
        & = & 
        \{ \ell \rightarrow con(rc_i,\ell,\Gamma,G)  ~\vert~ \ell \in f^{-1}(l_i) \}
        \\
     con(t_1 \rightarrow {pc}_1, ~\dots,~ t_k \rightarrow {pc}_k,\ell,\Gamma,G) 
        & = &  
        con(t_1 \rightarrow {pc}_1,\ell,\Gamma,G), \dots, con(t_k \rightarrow {pc}_k,\ell,\Gamma,G)
        \\
     con(pfx \rightarrow {pc},\ell,\Gamma,G) 
        & = &  
        pfx \rightarrow con(pc,\text{true},\ell,\Gamma,G)
        \\
     con(\$x \rightarrow {pc},\ell,\Gamma,G) 
        & = &  
        \{ pfx \rightarrow con(pc, l=\ell, \ell,\Gamma,G) ~\vert~ (pfx, l) \in \Gamma(x) \}
        \\
     con(ma_1, \dots, ma_k,o,\ell,\Gamma,G) 
        & = &
        con(ma_1,o,\ell,\Gamma,G), \dots, con(ma_k,o,\ell,\Gamma,G)
        \\

     con(n_1 : ({ns}_1, n_2) \rightarrow ({ns}_2, n_3),o,\ell,\Gamma,G) 
        & = & \textbf{if}~ ns_1 = \{G.s\} ~\text{and}~ o = \text{false} ~\textbf{then}~ \bullet \\
        &   & \textbf{else}~ n_1 : ( con({ns}_1,\ell,\Gamma,G), n_2) \rightarrow (con({ns}_2,\ell,\Gamma,G),n_3)

        \\
     con(\{ l_1, ~\dots,~ l_k \}, \ell, \Gamma,G) 
        & = &  
        \bigcup_i ~ \{ x ~\vert~ x \in f^{-1}(l_i),~ (x,\ell) \in G.E \}
        \\
\end{array} \]

@@

The goal of this section is to prove that the concretization and compilation functions commute. That is -- we can perform compilation directly over the abstraction and only substitute for the concrete values afterwards. First we need a few helper theorems about compilation.

@@

\begin{lem}
  For any map $\Gamma$ and regular expression $r$ over abstract locations, path $p \in \Lang(con(r,\Gamma)) \iff f(p) \in \Lang(r)$.
\end{lem}
\begin{proof}
By induction on the structure of $r$

\emph{Case $\emptyset$:}
  \[ \begin{array}{lll}
    p \in \Lang(con(\emptyset)) &\iff& f(p) \in \Lang(\emptyset) \\
    p \in \emptyset &\iff& f(p) \in \emptyset \\
  \end{array} \]

\emph{Case $l$:}
  \[ \begin{array}{lll}
    p \in \Lang(con(l)) &\iff& f(p) \in \Lang(l) \\
    p \in \Lang(\Sigma ~ f^{-1}(l)) &\iff& f(p) \in \Lang(l) \\
    p \in \bigcup f^{-1}(l) &\iff& f(p) \in \Lang(l) \\
    p \in f^{-1}(l) &\iff& f(p) \in \{ l \} \\
    p \in f^{-1}(l) &\iff& f(p) = l \\
    \text{by homomorphism} & & \\
  \end{array} \]

\emph{Case $r_1 \cup r_2$:}
  \[ \begin{array}{lll}
    p \in \Lang(con(r_1 \cup r_1)) &\iff& f(p) \in \Lang(r_1 \cup r_2) \\
    p \in \Lang(con(r_1) \cup con(r_1)) &\iff& f(p) \in \Lang(r_1 \cup r_2) \\
    p \in \Lang(con(r_1)) \cup \Lang(con(r_1)) &\iff& f(p) \in \Lang(r_1 \cup r_2) \\
    p \in \Lang(con(r_1)) \vee p \in \Lang(con(r_1)) 
       &\iff& 
       f(p) \in \Lang(r_1) \vee f(p) \in \Lang(r_2) \\
    \text{by cases + IH} & & \\
  \end{array} \]

\emph{Case $r_1 \cap r_2$:} 
  \[ \begin{array}{c}
    \text{symmetric to } \cup \text{ case}
  \end{array} \]

\emph{Case $!r$:}
  \[ \begin{array}{lll}
    p \in \Lang(con(!r)) &\iff& f(p) \in \Lang(!r) \\
    p \in \Lang(!con(r)) &\iff& f(p) \in \Lang(!r) \\
    p \in \Sigma^* - \Lang(con(r)) &\iff& f(p) \in \Sigma^* - \Lang(r) \\
    \text{by IH} & & \\
  \end{array} \]

\emph{Case $r^*$:}
  \[ \begin{array}{lll}
    p \in \Lang(con(r^*)) &\iff& f(p) \in \Lang(r^*) \\
    p \in \Lang(con(r)^*) &\iff& f(p) \in \Lang(r^*) \\
    p \in \bigcup_{i \in \mathbb{N}} \Lang(con(r))^i &\iff& f(p) \in \bigcup_{i \in \mathbb{N}} \in \Lang(r)^i \\
    \text{Follows from IH and definition of } \Lang(r)^i & & \\
  \end{array} \]

@@

\begin{lem}
  Consider the PG created from compiling the constraint $p = (t ~\Path~ r_1 ~\Prefer~,\dots, ~\Prefer~ r_k)$ with state machine $M^A_i$ for each $r_i$. We know that, for each $(pfx ~\Path~ r'_1 ~\Prefer~,\dots, ~\Prefer~ r'_k) \in con(p)$ where $r'_i$ is of the form $r \cap \text{end}(L)$ we can constuct state machine $M_i$ for $r'_i$ over the same states in the following way:

@@

    \[ \begin{array}{lcl}
      con(p) &=& pfx_1 ~\Path~ con(r_1) \cap \text{end}(l_1), ~\Prefer~ \dots ~\Prefer~ con(r_k) \cap \text{end}(l_1)  \\
             & & \dots, \\
             & & pfx_n ~\Path~ con(r_1) \cap \text{end}(l_n), ~\Prefer~ \dots ~\Prefer~ con(r_k) \cap \text{end}(l_n)
    \end{array} \]

@@

    Assume $M_i$ matches $p$. Then this means that $M^A_i$ matches $f(p)$. If we have a trace of string of the form $ p = x_1 \cdot \dots \cdot x_n$, then $f(p) = f(x_1) \cdot \dots \cdot f(x_n)$. For each transition $\sigma(q,l) = q'$ in the concrete automaton, we have transition $\sigma(q,f(l)) = q'$ in the abstract automaton, and they have the same final states, so this trace is accepting for $M^A_i$. Because $M^A_i$ matches $f(p)$, this means that $f(p) \in \Lang(r_i)$. From our above lemma, this means that $p \in \Lang(con(r_i))$. We also know that, since $L = \{ l_i \}$, the first transition $\sigma(q_0,l_i)$ is the only transition allowed from the initial state for $M_i$. So this means that $p \in \Lang(\text{end}(l_i))$. Since we know that $p \in \Lang(con(r_i))$ and $p \in \Lang(\text{end}(l_i))$, we know that $p \in \Lang(con(r_i) \cap \text{end}(l_i))$ and thus $p \in \Lang(r'_i)$.

@@

    \[ \begin{array}{lcl}
      con(p) &=& pfx_1 ~\Path~ con(r_1) \cap \text{end}(\Sigma^*), ~\Prefer~ \dots ~\Prefer~ con(r_k) \cap \text{end}(\Sigma^*) \\
    \end{array} \]

@@

    \[ \begin{array}{lll}
      M ~\text{matches}~ p &\iff& M^A ~\text{matches}~ f(p) \\
                         &\iff& f(p) \in \Lang(r) \\
                         &\iff& p \in \Lang(con(r)) \\
    \end{array} \]%

@@

\subsection{Product Graph}

@@

\begin{lem}
  If $f_{pg}(n) = N$, then $P(n) = P^A(N)$.

@@

\begin{lem}
  If, for abstract product graph $PG$, if we have the following:

@@

\begin{defn}
  Assign $ord(m) = ord^A(f_{pg}(m))$ as increasing integers according to the total ordering for $\leq$.
  Clearly $ord(m) \leq ord(m') \iff m \leq m'$ and $ord(f_{pg}(m)) \leq ord(f_{pg}(m')) \iff f_{pg}(m) \leq f_{pg}(m')$
\end{defn}

\begin{defn}
  The previous theorem tells us that the total ordering between node preferences is preserved under the lifted graph homomorphism $f_{pg}$. 
  We use this fact to define an ordering ($ord : V \rightarrow \mathbb{N}$) that maps product graph nodes to numbers reflecting the total ordering such that $ord(m) = ord(f(m))$ for all product graph nodes $m$.
\end{defn}

\subsection{Substitution}

@@

\vspace{2em}
\begin{thm}
  $compile(con(pol)) = con(compile(pol))$

@@

    \[ \begin{array}{lcl}
      con(pol) & = & con(p_1,\dots,p_n) \\
               & = & con(p_1), \dots, con(p_n) \\
               & = & con(t_1 ~\Path~ r_{11} ~\Prefer~,\dots, ~\Prefer~ r_{1k}), \\
               &   & \dots, \\
               &   & con(t_n ~\Path~ r_{n1} ~\Prefer~,\dots, ~\Prefer~ r_{nk}) \\
    \end{array} \]

@@

    \[ \begin{array}{lcl}
        con({pfx}_{i1} ~\Path~ r_{i1} ~\Prefer~,\dots, ~\Prefer~ r_{ik}) 
           & = & {pfx}_{i1} ~\Path~ con(r_{i1}) ~\Prefer~,\dots, ~\Prefer~ con(r_{ik}) \\
    \end{array} \]

@@

    \[ \begin{array}{lcl}
        con(\$x_{i} ~\Path~ r_{i1} ~\Prefer~,\dots, ~\Prefer~ r_{ik}) 
            & = & {pfx}_{i1} ~\Path~ con(r_{i1}) \cap \text{end}(l_{i1}) ~\Prefer~,\dots, ~\Prefer~ con(r_{ik}) \cap \text{end}(l_{i1}), \\
            &   & \dots, \\ 
            &   & {pfx}_{ij} ~\Path~ con(r_{i1}) \cap \text{end}(l_{ij}) ~\Prefer~,\dots, ~\Prefer~ con(r_{ik}) \cap \text{end}(l_{ij}), \\
            &   & \\
            &   & \text{for each } (pfx_{ij}, l_{ij}) \in \Gamma(x) \\
    \end{array} \]

    Next we compute $compile(con(pol))$:

    \[ \begin{array}{lcl}
        compile(con(pol)) &=& compile_{ABGP}( \\
                          & & ~~~~ compile_{PG}(pfx_{11} ~\Path~ r'_{111} ~\Prefer~,\dots, ~\Prefer~ r'_{11k} ), \\
                          & & ~~~~ \dots, \\
                          & & ~~~~ compile_{PG}(pfx_{1j} ~\Path~ r'_{1j1} ~\Prefer~,\dots, ~\Prefer~ r'_{1jk} ), \\
                          & & ~~~~ \dots, \\
                          & & ~~~~ compile_{PG}(pfx_{i1} ~\Path~ r'_{i11} ~\Prefer~,\dots, ~\Prefer~ r'_{i1k} ), \\
                          & & ~~~~ \dots, \\
                          & & ~~~~ compile_{PG}(pfx_{ij} ~\Path~ r'_{ij1} ~\Prefer~,\dots, ~\Prefer~ r'_{ijk} ) \\
                          & & ) \\
    \end{array} \]

    This results in a series of prefixes, product graphs, and orderings of the form: $(pfx_{ij}, PG_{ij}, ord_{ij})$.

@@

    \[ \begin{array}{lcl}
        compile(pol) &=& compile_{ABGP}( \\
                     & & ~~~~ compile_{PG}(t_1 ~\Path~ r_{11} ~\Prefer~,\dots, ~\Prefer~ r_{1k} ), \\
                     & & ~~~~ \dots, \\
                     & & ~~~~ compile_{PG}(t_i ~\Path~ r_{i1} ~\Prefer~,\dots, ~\Prefer~ r'_{ik} ), \\
                     & & ) \\
    \end{array} \]

@@

  \[ \begin{array}{l}
     con(\textbf{compile}( (t_1,PG^A_1,ord^A_1), \dots, (t^A_i,PG^A_i,ord^A_i) )) \\
  \end{array} \]%

>>>>

\documentclass[twocolumn, openany]{sig-alternate-10pt}
%\documentclass[twocolumn]{article}
%\documentclass[10pt]{sigalternate052015}

@@

\onecolumn

@@

\section{Definitions}

@@

The full \sysname syntax as well as expansions from constraints into regular expressions are shown in Figure~\ref{fig:syntax}. The language includes constraints of the form $\CD{\Agg(pfx, \ensuremath{r_1 \rightarrow r_2})}$ that say that aggregation for summary prefix $\CD{pfx}$ will occur from any single location matching $\CD{\ensuremath{r_1}}$ to any location matching $\CD{\ensuremath{r_2}}$. For simplicity, we prove the substitution property for \sysname for the fragment without aggregation.

@@

We define syntax for an abstraction of BGP configurations -- called ABGP -- in Figure~\ref{fig:abgp-syntax}. An ABGP policy consists of a map from topology locations $l$ to router configurations $rc$. Each router configuration $rc$ is a sequence of prefix (templates) $t$ and their corresponding prefix configuration $pc$. A prefix configuration $pc$ is a sequence of match actions $ma$. Each match action $ma$ consists of a preference value $n_1$, followed by a set of imports from neighbors $ns_1$ and community value (\IE, state of the product graph) $n_2$, as well as export neighbors $ns_2$ and the updated community value $n_3$.

@@

@@

The function $compile_{ABGP}$ then takes tuples $(t_i, PG_i, ord_i)$ and returns an ABGP policy. It looks at each incoming neighbor with the same community state $q_n$ and matches any of those neighbor with the preference provided by the ordering $ord$ obtained from the search for local preferences. It then exports this advertisement to each adjacent peer along an outgoing edge and adds the community value for the current state $q_m$.

We assume a particular router $l$ appears at most once in any abgp specification.
We often build configs using set-builder notation.  For instance,
$\{l \rightarrow rc ~\vert~ l \in V \wedge p(l,rc)\}$ denotes the abgp policy

where $l_1, ..., l_k$ are the nodes in the topology
and each $rc_{ij}$ satisfies $p(l_i,rc_{ij})$.

@@

We define what it means to concretize an abstract \sysname policy. 
Concretization takes as input, a policy and a context $\Gamma$ mapping from a template prefix to a set of pairs of a concrete prefix and a concrete location where the prefix is owned.

\[ \begin{array}{lcl}
  con(\emptyset,\Gamma,f)                        & = & \emptyset \\
  con(l,\Gamma,f)                                & = & \Sigma ~ f^{-1}(l) \\
  con(r_1 \cup r_2,\Gamma,f)                     & = & con(r_1,\Gamma,f) \cup con(r_2,\Gamma,f) \\
  con(r_1 \cap r_2,\Gamma,f)                     & = & con(r_1,\Gamma,f) \cap con(r_2,\Gamma,f) \\
  con(!r,\Gamma,f)                               & = & !con(r,\Gamma,f) \\
  con(r^*,\Gamma,f)                              & = & con(r,\Gamma,f)^* \\
  con(pfx \Rightarrow r_1, \dots, r_k,\Gamma,f)  & = & pfx \Rightarrow con(r_1,\Gamma,f), \dots, con(r_k,\Gamma,f) \\
  con(\$x \Rightarrow r_1, \dots, r_k,\Gamma,f)  & = & 
       \{ pfx \Rightarrow con(r_1,\Gamma,f) \cap \text{end}(l), 
          \dots, 
          con(r_k,\Gamma,f) \cap \text{end}(l) ~\vert~ (pfx,l) \in \Gamma(x) \} \\
  %& & ~~~~~~~~~~~~~~~ \dots, \\
  %& & ~~~~~~~~~~~~~~~ con(r_k,\Gamma,G) \cap \text{end}(l) ~\vert~ (pfx,l) \in \Gamma(x),  ~l \in G.V \} \\
  con(p_1, \dots, p_n, \Gamma, f)                & = & con(p_1,\Gamma,f), \dots, con(p_n,\Gamma,f) \\
\end{array} \]

For each regular expression $r$, we replace each abstract location with the sum over its corresponding concrete locations under the inverse homomorphism $f^{-1}$. For each template variable, we replace it with a new entry for each of its corresponding concrete values under the supplied mapping $\Gamma$. We also intersect the resulting concretized regular expression with $\text{end}(l)$ to capture the fact that traffic is owned by the concrete location $l$. \textbf{Note}: we need the side condition that $\text{end}(l) \cap con(r_i,\Gamma) \neq \emptyset$ if $con(r_i,\Gamma) \neq \emptyset$.
We can also define concretization over the ABGP policy as:

\[ \begin{array}{lcl}
     con(l_1 \rightarrow {rc}_1, ~\dots,~ l_k \rightarrow {rc}_k,\Gamma,f,G) 
        & = & 
        \{ \ell \rightarrow con(rc_i,\ell,\Gamma,f,G)  ~\vert~ \ell \in f^{-1}(l_i) \}
        \\
     con(t_1 \rightarrow {pc}_1, ~\dots,~ t_k \rightarrow {pc}_k,\ell,\Gamma,f,G) 
        & = &  
        con(t_1 \rightarrow {pc}_1,\ell,\Gamma,f,G), \dots, con(t_k \rightarrow {pc}_k,\ell,\Gamma,f,G)
        \\
     con(pfx \rightarrow {pc},\ell,\Gamma,f,G) 
        & = &  
        pfx \rightarrow con(pc,\text{true},\ell,\Gamma,f,G)
        \\
     con(\$x \rightarrow {pc},\ell,\Gamma,f,G) 
        & = &  
        \{ pfx \rightarrow con(pc, l=\ell, \ell,\Gamma,f,G) ~\vert~ (pfx, l) \in \Gamma(x) \}
        \\
     con(ma_1, \dots, ma_k,o,\ell,\Gamma,f,G) 
        & = &
        con(ma_1,o,\ell,\Gamma,f,G), \dots, con(ma_k,o,\ell,\Gamma,f,G)
        \\

     con(n_1 : ({ns}_1, n_2) \rightarrow ({ns}_2, n_3),o,\ell,\Gamma,f,G) 
        & = & \textbf{if}~ ns_1 = \{G.s\} ~\text{and}~ o = \text{false} ~\textbf{then}~ \bullet \\
        &   & \textbf{else}~ n_1 : ( con({ns}_1,\ell,\Gamma,f,G), n_2) \rightarrow (con({ns}_2,\ell,\Gamma,f,G),n_3)

        \\
     con(\{ l_1, ~\dots,~ l_k \}, \ell, \Gamma,f,G) 
        & = &  
        \bigcup_i ~ \{ x ~\vert~ x \in f^{-1}(l_i),~ (x,\ell) \in G.E \}
        \\
\end{array} \]

We use the symbol $\bullet$ to denote that a particular value in a sequence is removed from the sequence.

@@

The goal of this section is to prove that the concretization and compilation functions commute: 
$$con(compile(pol),\Gamma,f,G) = compile(con(pol,\Gamma,f))$$ 
That is -- we can perform compilation directly over the abstraction and only substitute for the concrete values on after compilation is complete. Note that the theorem states that the resulting ABGP policies are actually syntactically equivalent and not semantically equivalent. First we need a few helper theorems about compilation.

@@

\vspace{1em}
\begin{lem}
  For any $\Gamma$, $f$, and $r$, path $p \in \Lang(con(r,\Gamma,f)) \iff f(p) \in \Lang(r)$.
\end{lem}
\begin{proof}
By induction on the structure of $r$

\emph{Case $\emptyset$:}
  \[ \begin{array}{lll}
    p \in \Lang(con(\emptyset,\Gamma,f)) &\iff& f(p) \in \Lang(\emptyset) \\
    p \in \emptyset &\iff& f(p) \in \emptyset \\
  \end{array} \]

\emph{Case $l$:}
  \[ \begin{array}{lll}
    p \in \Lang(con(l,\Gamma,f)) &\iff& f(p) \in \Lang(l) \\
    p \in \Lang(\Sigma ~ f^{-1}(l)) &\iff& f(p) \in \Lang(l) \\
    p \in \bigcup f^{-1}(l) &\iff& f(p) \in \Lang(l) \\
    p \in f^{-1}(l) &\iff& f(p) \in \{ l \} \\
    p \in f^{-1}(l) &\iff& f(p) = l \\
    \text{by homomorphism} & & \\
  \end{array} \]

\emph{Case $r_1 \cup r_2$:}
  \[ \begin{array}{lll}
    p \in \Lang(con(r_1 \cup r_1,\Gamma,f)) &\iff& f(p) \in \Lang(r_1 \cup r_2) \\
    p \in \Lang(con(r_1,\Gamma,f) \cup con(r_1,\Gamma,f)) &\iff& f(p) \in \Lang(r_1 \cup r_2) \\
    p \in \Lang(con(r_1,\Gamma,f)) \cup \Lang(con(r_1,\Gamma,f)) &\iff& f(p) \in \Lang(r_1 \cup r_2) \\
    p \in \Lang(con(r_1,\Gamma,f)) \vee p \in \Lang(con(r_1,\Gamma,f)) 
       &\iff& 
       f(p) \in \Lang(r_1) \vee f(p) \in \Lang(r_2) \\
    \text{by cases + IH} & & \\
  \end{array} \]

\emph{Case $r_1 \cap r_2$:} 
  \[ \begin{array}{c}
    \text{symmetric to } \cup \text{ case with } \wedge \text{ instead of } \vee
  \end{array} \]

\emph{Case $!r$:}
  \[ \begin{array}{lll}
    p \in \Lang(con(!r,\Gamma,f)) &\iff& f(p) \in \Lang(!r) \\
    p \in \Lang(!con(r,\Gamma,f)) &\iff& f(p) \in \Lang(!r) \\
    p \in \Sigma^* - \Lang(con(r,\Gamma,f)) &\iff& f(p) \in \Sigma^* - \Lang(r) \\
    \text{by IH} & & \\
  \end{array} \]

\emph{Case $r^*$:}
  \[ \begin{array}{lll}
    p \in \Lang(con(r^*,\Gamma,f)) &\iff& f(p) \in \Lang(r^*) \\
    p \in \Lang(con(r,\Gamma,f)^*) &\iff& f(p) \in \Lang(r^*) \\
    p \in \bigcup_{i \in \mathbb{N}} \Lang(con(r,\Gamma,f))^i &\iff& f(p) \in \bigcup_{i \in \mathbb{N}} \in \Lang(r)^i \\
    \text{Follows from IH and definition of } \Lang(r)^i & & \\
  \end{array} \]

@@

\begin{lem}
  Consider the PG created from compiling the constraint $p = (t ~\Path~ r_1 ~\Prefer~,\dots, ~\Prefer~ r_k)$ with state machine $M^A_i$ for each $r_i$. We know that, for each $(pfx ~\Path~ r'_1 ~\Prefer~,\dots, ~\Prefer~ r'_k) \in con(p,\Gamma,f)$ where $r'_i$ is of the form $r \cap \text{end}(L)$ we can constuct state machine $M_i$ for $r'_i$ over the same states in the following way:

@@

    \[ \begin{array}{lcl}
      con(p) &=& pfx_1 ~\Path~ con(r_1,\Gamma,f) \cap \text{end}(l_1), ~\Prefer~ \dots ~\Prefer~ con(r_k,\Gamma,f) \cap \text{end}(l_1)  \\
             & & \dots, \\
             & & pfx_n ~\Path~ con(r_1,\Gamma,f) \cap \text{end}(l_n), ~\Prefer~ \dots ~\Prefer~ con(r_k,\Gamma,f) \cap \text{end}(l_n)
    \end{array} \]

@@

    Assume $M_i$ matches $p$. Then this means that $M^A_i$ matches $f(p)$. If we have a trace of string of the form $ p = x_1 \cdot \dots \cdot x_n$, then $f(p) = f(x_1) \cdot \dots \cdot f(x_n)$. For each transition $\sigma(q,l) = q'$ in the concrete automaton, we have transition $\sigma(q,f(l)) = q'$ in the abstract automaton, and they have the same final states, so this trace is accepting for $M^A_i$. Because $M^A_i$ matches $f(p)$, this means that $f(p) \in \Lang(r_i)$. From our above lemma, this means that $p \in \Lang(con(r_i,\Gamma,f))$. We also know that, since $L = \{ l_i \}$, the first transition $\sigma(q_0,l_i)$ is the only transition allowed from the initial state for $M_i$. So this means that $p \in \Lang(\text{end}(l_i))$. Since we know that $p \in \Lang(con(r_i,\Gamma,f))$ and $p \in \Lang(\text{end}(l_i))$, we know that $p \in \Lang(con(r_i,\Gamma,f) \cap \text{end}(l_i))$ and thus $p \in \Lang(r'_i)$.

@@

    \[ \begin{array}{lcl}
      con(p,\Gamma,f) &=& pfx_1 ~\Path~ con(r_1,\Gamma,f) \cap \text{end}(\Sigma^*), ~\Prefer~ \dots ~\Prefer~ con(r_k,\Gamma,f) \cap \text{end}(\Sigma^*) \\
    \end{array} \]

@@

    \[ \begin{array}{lll}
      M ~\text{matches}~ p &\iff& M^A ~\text{matches}~ f(p) \\
                         &\iff& f(p) \in \Lang(r) \\
                         &\iff& p \in \Lang(con(r,\Gamma,f)) \\
    \end{array} \]%

@@

\vspace{1em}
\subsection{Product Graph}

@@

\vspace{1em}
\begin{lem}
  If $f_{pg}(n) = N$, then $P(n) = P^A(N)$.

@@

\vspace{1em}
\begin{lem}
  If, for abstract product graph $PG$, if we have the following:

@@

\vspace{1em}
\begin{defn}
  Assign $ord(m) = ord^A(f_{pg}(m))$ as increasing integers according to the total ordering for $\leq$.
  Clearly $ord(m) \leq ord(m') \iff m \leq m'$ and $ord(f_{pg}(m)) \leq ord(f_{pg}(m')) \iff f_{pg}(m) \leq f_{pg}(m')$
\end{defn}

\vspace{1em}
\begin{defn}
  The previous theorem tells us that the total ordering between node preferences is preserved under the lifted graph homomorphism $f_{pg}$. 
  We use this fact to define an ordering ($ord : V \rightarrow \mathbb{N}$) that maps product graph nodes to numbers reflecting the total ordering such that $ord(m) = ord(f(m))$ for all product graph nodes $m$.
\end{defn}

\vspace{1em}
\subsection{Substitution}

@@

\vspace{2em}
\begin{thm}
  For any $\Gamma$, $f$, $G$ such that $\Gamma$ is well-formed with respect to $G$,
  $$con(compile(pol),\Gamma,f,G) = compile(con(pol,\Gamma,f))$$

@@

    \[ \begin{array}{lcl}
      con(pol,\Gamma,f) & = & con(p_1,\dots,p_n,\Gamma,f) \\
                        & = & con(p_1,\Gamma,f), \dots, con(p_n,\Gamma,f) \\
                        & = & con(t_1 ~\Path~ r_{11} ~\Prefer~,\dots, ~\Prefer~ r_{1k},\Gamma,f), \\
                        &   & \dots, \\
                        &   & con(t_n ~\Path~ r_{n1} ~\Prefer~,\dots, ~\Prefer~ r_{nk},\Gamma,f) \\
    \end{array} \]

@@

    \[ \begin{array}{ll}
          & con({pfx}_{i1} ~\Path~ r_{i1} ~\Prefer~,\dots, ~\Prefer~ r_{ik},\Gamma,f) \\
        = & {pfx}_{i1} ~\Path~ con(r_{i1},\Gamma,f) ~\Prefer~,\dots, ~\Prefer~ con(r_{ik},\Gamma,f) \\
    \end{array} \]

@@

    \[ \begin{array}{lcl}
        con(\$x_{i} ~\Path~ r_{i1} ~\Prefer~,\dots, ~\Prefer~ r_{ik},\Gamma,f) 
            & = & {pfx}_{i1} ~\Path~ con(r_{i1},\Gamma,f) \cap \text{end}(l_{i1}) ~\Prefer~,\dots, ~\Prefer~ con(r_{ik},\Gamma,f) \cap \text{end}(l_{i1}), \\
            &   & \dots, \\ 
            &   & {pfx}_{ij} ~\Path~ con(r_{i1},\Gamma,f) \cap \text{end}(l_{ij}) ~\Prefer~,\dots, ~\Prefer~ con(r_{ik},\Gamma,f) \cap \text{end}(l_{ij}), \\
            &   & \\
            &   & \text{for each } (pfx_{ij}, l_{ij}) \in \Gamma(x) \\
    \end{array} \]

    Next we compute $compile(con(pol,\Gamma,f))$:

    \[ \begin{array}{ll}
        & compile(con(pol,\Gamma,f))  \\
                          & \\
                         =& compile_{ABGP}( \\
                          &  ~~~~ compile_{PG}(pfx_{11} ~\Path~ r'_{111} ~\Prefer~,\dots, ~\Prefer~ r'_{11k} ), \\
                          &  ~~~~ \dots, \\
                          &  ~~~~ compile_{PG}(pfx_{1j} ~\Path~ r'_{1j1} ~\Prefer~,\dots, ~\Prefer~ r'_{1jk} ), \\
                          &  ~~~~ \dots, \\
                          &  ~~~~ compile_{PG}(pfx_{i1} ~\Path~ r'_{i11} ~\Prefer~,\dots, ~\Prefer~ r'_{i1k} ), \\
                          &  ~~~~ \dots, \\
                          &  ~~~~ compile_{PG}(pfx_{ij} ~\Path~ r'_{ij1} ~\Prefer~,\dots, ~\Prefer~ r'_{ijk} ) \\
                          &  ) \\
    \end{array} \]

    \vspace{.5em}
    This results in a series of prefixes, product graphs, and orderings of the form: $(pfx_{ij}, PG_{ij}, ord_{ij})$.

@@

    \[ \begin{array}{ll}
        & compile(pol)  \\
                      & \\
                     =& compile_{ABGP}( \\
                      & ~~~~ compile_{PG}(t_1 ~\Path~ r_{11} ~\Prefer~,\dots, ~\Prefer~ r_{1k} ), \\
                      & ~~~~ \dots, \\
                      & ~~~~ compile_{PG}(t_i ~\Path~ r_{i1} ~\Prefer~,\dots, ~\Prefer~ r'_{ik} ), \\
                      & ) \\
    \end{array} \]

@@

  \[ \begin{array}{l}
     con(\textbf{compile}( (t_1,PG^A_1,ord^A_1), \dots, (t^A_i,PG^A_i,ord^A_i) ), \Gamma,f,G) \\
  \end{array} \]%
